Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-31 ba_resubmit_template_files/response_to_reviewers3.tex

\pointRaised{AE}{Line 80 on p. 3 says: “For ease of readability, we follow the convention established by \cite{sadinle_bayesian_2017} and say “record $i \in X_1$” rather than the more compact $x_{1i}$.” Taking this at face value implies that, in any sentence, one could swap “record $i \in X_1$” for “$x_{1i}$,” which clearly is not true.  So, as it stands, the sentence does little to improve ease of readability.  In fact, if the point is that “$x_{1i}$” will never be used again, why is the notation introduced in the first place?}

%%% RCS: Thank the Editor, explain the change. I have removed repetition and shortened this bit.

\reply{
We now refer to the two data files as $A$ and $B$. The updated material now reads:

``Consider two data files $A$ and $B$ comprising $n_A$ and $n_B$ records, respectively, and including $F$ linkage variables measured in both files. For $i=1, \dots, n_A$, let record $i$ be given by $A_i = (A_{i1}, \dots, A_{iF})$, so that $A = (A_i : i = 1, \dots, n_A)$.  Similarly, for $j=1, \dots, n_B$, let record $j$ be given by $B_j = (B_{j1}, \dots, B_{jF})$, so that $B = (B_j : j = 1, \dots, n_B)$.  Without loss of generality, denote files such that $n_A \geq n_B$". See Section 2. 
}

@@

\setcounter{responsectr}{0}
\section{Associate Editor Comments}

	\pointRaised{R}{%
	For the missing data treatment now included just before Section 2.1, is the assumption truly missing at random, or missing completely at random? Or, does this distinction not matter because of the independence assumed across elements of the comparison vector?}

	\reply{
	\textcolor{teal}{The reviewer is correct that the distinction does not matter between MCAR and MAR. We have included the following explanation of missingness in Section 2.}
%		Because we assume that the agreement level for each field is conditionally independent given the matching status, MAR and MCAR are equivalent here. For simplicity, we have chosen to use MCAR in the article. 
%		We have included the following explanation of missingness in Section 2.

@@

	``In the construction of comparison vectors, it is common to encounter missing information in record $A_i$ or $B_j$. As a result, the comparison vector $\mathbf{\gamma}_{ij}$ will have missing values. We assume that this missingness occurs completely at random (MCAR, per \cite{LittleRubin2002}). To notate a missing value in any $\gamma_{ij}^f$, we use $I_{obs}(\gamma_{ij}^f)=1$ when $\gamma_{ij}^f$ is observed and $I_{obs}(\gamma_{ij}^f)=0$ otherwise. With the MCAR assumption, we can marginalize over the missing data, and do all computation simply using the observed data."
	}

	\pointRaised{R}{%
	Appendix 8.2: I appreciate the streamlining of the discussion of the proposed algorithms and think it was a good choice to move the full derivation to an appendix. However, I do not follow the re-expression of the pmf for $\Gamma_{.j}$. First, the opening square brackets are still misplaced throughout. In the second line of this derivation, the authors divide the expression by a product of the element-wise conditional probabilities of a match in the comparison vector (u), raised by an indicator that the element of the comparison vector equals a particular value. Perhaps I misunderstand, but I believe this product is not constant in $\Gamma_{.j}$ or $u$, and so the total expression is not proportional to the line above, as interpreted as a pmf. I think that the end effect is that the last line of the newly expressed pmf is missing a factor of $\prod_i \prod_f \prod_l u_{fl}^{I(\gamma_{ij}^f = l) I_{obs}(\gamma_{ij}^f)}$ regardless of the value of $z_j$.}

\reply{%
	The square brackets have been corrected.

	We have revised the derivation of the full conditional distribution of $Z_j$, separately handling the case when $B_j$ has a match and when it does not. Refer to \textcolor{teal}{Supplement}~A for this extended derivation.
	}

@@

%\reply{No, in \text{fabl}, we do not integrate out $\pi$ as done in \cite{sadinle_bayesian_2017} because this leads to a sequential sampler. 
%
%(1) Yes, our alternative approach is different than directly integrating over the prior distribution $\pi.$ 
%%We have attempted to make this more clear in our revised version. 
%In short, our prior distribution over $\bm{Z}$ leads to a Gibbs sampler that leads to parallel updates, which contrasts that of \cite{sadinle_bayesian_2017}. Of course, we could integrate out $\pi$ in our approach, however, this leads to sequential updates, which would be slow in practice. See Appendix A, page 27. 
%
%(2) Yes, our alternative approach is justified. We provide a justification in Appendix A, page 27 regarding why the updates are independent and not sequential. Thank you for the excellent questions, which have greatly improved our paper. 
%
%}

\pointRaised{R}{%
	I do not understand the statement just below Equation (10): “When j has no match in $X_1$, we write $(n_1 +j, j) \in h_{P+1}$” My understanding of these patterns is that they are based on observed comparison vectors without consideration of Z (matches). In the second paragraph of Section 4.3, the H notation includes the matches (Z), in notation and definition that seems to conflict with the statement just below Equation (10). This also comes into play in Equation (16).}

	%% RCS: Tried to answer this from the original paper and the updated paper. Tried to make it shorter and close it out very quickly.

	\reply{Yes, the comparison vectors are created (and therefore, patterns are assigned) without regard to $\bm{Z}$. We have removed that sentence, and updated the equations in Section 4.3 to avoid confusion.}

### 2023-07-31 ba_resubmit_template_files/response_to_reviewers3.tex

	\title{Response to Reviewer Comments}
	\maketitle

We thank the Editor and Associate Editor for their assessment and constructive feedback.

%Thank you for the thoughtful feedback. We have made several broad changes to address the Editor's and Associate Editor's overall critiques, and have addressed each specific comment from the reviewer.

\section{Editor Comments}

\pointRaised{E}{I must add that reading the paper still feels like a chore, in part because the notation is so heavy, which may be hard to avoid, but also, in part, because some wording choices make certain sentences hard to parse, which can certainly be improved.}

@@

``Consider two data files $A$ and $B$ comprising $n_A$ and $n_B$ records, respectively, and including $F$ linkage variables measured in both files. For $i=1, \dots, n_A$, let record $i$ be given by $A_i = (A_{i1}, \dots, A_{iF})$, so that $A = (A_i : i = 1, \dots, n_A)$.  Similarly, for $j=1, \dots, n_B$, let record $j$ be given by $B_j = (B_{j1}, \dots, B_{jF})$, so that $B = (B_j : j = 1, \dots, n_B)$.  Without loss of generality, denote files such that $n_A \geq n_B$". See Section 2. 
}

\setcounter{responsectr}{0}
\section{Associate Editor Comments}

	\pointRaised{R}{%
	For the missing data treatment now included just before Section 2.1, is the assumption truly missing at random, or missing completely at random? Or, does this distinction not matter because of the independence assumed across elements of the comparison vector?}

	\reply{
	The reviewer is correct that the distinction does not matter between MCAR and MAR. We have included the following explanation of missingness in Section 2.
%		Because we assume that the agreement level for each field is conditionally independent given the matching status, MAR and MCAR are equivalent here. For simplicity, we have chosen to use MCAR in the article. 
%		We have included the following explanation of missingness in Section 2.

### 2023-07-31 ba_resubmit_template_files/main.tex
fix name on page one.
updates to paper and response to reviewers.

	\subsection{Civilian Casualties from the El Salvadoran Civil War}
	\label{el_salvador}

@@

\begin{supplement}
\stitle{Supplementary Material of ``Efficient and Scalable Bipartite Matching with
Fast Beta Linkage (fabl)." See the .pdf document}
\sdescription{}
\end{supplement}

>>>>

	\subsection{Civilian Killings from the El Salvadoran Civil War}
	\label{el_salvador}

@@

\begin{supplement}
\stitle{Supplementary Material of ``Efficient and Scalable Bipartite Matching with
Fast Beta Linkage (fabl).'' See the .pdf document}
\sdescription{}
\end{supplement}
